### 2024-08-22 paper.tex
actual progress on alternative characterization of bs

\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
Let \(B_{I, (\rho_i)}'\) be the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
    \item For \(i \notin I\), let \(S = \{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    If \(S = \emptyset\), then \(p_i \leq \lambda_i - q_{i_0}\).
    Otherwise, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k = \min S\).
\end{itemize}
\begin{lemma}\label{alternative_bs}
    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\).
\end{lemma}
\begin{proof}
    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
    Let \(b \in B_{I, (\rho_i)}\).
    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
    Now, I claim that for every \(s \in \{0, ..., r\}\), either 
    So, let \(i \notin I\), and let \(S = \{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    We have two cases: either \(S\) is empty, or not.
    \par If \(S\) is empty

>>>>

\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
Let \(B_{I, (\rho_i)}'\) be the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
    \item For \(i \notin I\), let \(S = \{k \in \{1, ..., r + 1\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    If \(S = \emptyset\), then \(p_i \leq \lambda_i - q_{i_0}\).
    If \(r + 1 \in S\), then \(p_i \leq p_{i_{r + 1}}\).
    Otherwise, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k = \max S\).\footnote{I could remove the edge cases if I define \(q_{i_{-1}}\) and \(q_{i_{r + 1}}\)...}
\end{itemize}
\begin{lemma}\label{alternative_bs}
    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\).
\end{lemma}
\begin{proof}
    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
    Let \(b \in B_{I, (\rho_i)}\).
    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
    \par First suppose \(S = \emptyset\).
    Then if we had \(q_i < q_{i_0}\), this would entail \(p_i \leq \max_{j : q_j < q_{i_0}} = p_{i_1}\).
    But then \(\lambda_i = p_i + q_i < q_{i_0} + p_{i_1}\), contradicting that \(1 \notin S\).
    Hence \(q_i \geq q_{i_0}\), and therefore \(p_i \leq \lambda_i - q_{i_0}\).
    \par Now suppose \(r + 1 \in S\).
    Then we have \(q_{i_r} + p_{i_{r + 1}} > \lambda_i\).
    Then 
    \par Let \(k \in \{1, ..., r + 1\} \setminus S\).
    We have \(q_{i_{k - 1}} + p_{i_k} \leq \lambda_i\).
    Suppose we had \(q_i < q_{i_{k - 1}}\).
    Then \(p_i \leq \max_{j : q_j < q_{i_{k - 1}}} p_j = p_{i_k}\).
    But then \(p_i + q_i < q_{i_{k - 1}} + p_{i_k} \leq \lambda_i\), which is nonsense.

    \par There are a few cases: either \(q_i \geq q_{i_0}\), or there's some \(k\) with \(q_{i_{k - 1}} > q_i \geq q_{i_k}\), or else \(q_{i_r} > q_i\).
    In the case that \(q_i \geq q_{i_0}\) we have \(p_i \leq \lambda_i - q_{i_0}\).
    In the case that \(q_{i_{k - 1}} > q_i \geq q_{i_{k - 1}}\), we have \(p_i \leq \lambda_i - q_{i_k}\), and also \(p_i \leq \max_{j : q_j < q_{i_{k - 1}}} p_j = p_{i_k}\).
    That is, \(p_i \leq \min(\lambda_i - q_{i_k}, p_{i_k})\).
    In the case that \(q_{i_r} > q_i\), we have \(p_i \leq \max_{j : q_j < q_{i_r}} p_j = p_{i_{r + 1}}\).
    So,
    \[p_i \leq \max(\lambda_i - q_{i_0}, \max_k \min(\lambda_i - q_{i_k}, p_{i_k}), p_{i_{r + 1}})\]

    For \(s \in \{1, ..., r + 1\}\), we have two cases: either \(q_i < q_{i_s}\), or \(q_i \geq q_{i_s}\).

    then \(p_i \leq \max_{j : q_j < q_{i_s}} p_j = p_{i_{s + 1}}\).
    So, either \(\)

    Now, I claim that for every \(s \in \{0, ..., r\}\), either 
    So, let \(i \notin I\), and let \(S = \{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    We have two cases: either \(S\) is empty, or not.
    \par If \(S\) is empty
